---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# caffeR: a wrapper to 'caffe'

[![Build Status](https://travis-ci.org/cnaumzik/caffeR.svg?branch=master)](https://travis-ci.org/cnaumzik/caffeR)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/caffeR)](https://cran.r-project.org/package=caffeR)
[![Coverage Status](https://img.shields.io/codecov/c/github/cnaumzik/caffeR/master.svg)](https://codecov.io/github/cnaumzik/caffeR?branch=master)

**SentimentAnalysis** performs a **sentiment analysis** of textual contents in R. This implementation utilizes various existing dictionaries, such as General Inquirer, Harvard IV or Loughran-McDonald. Furthermore, it can also create customized dictionaries. The latter uses LASSO regularization as a statistical approach to select relevant terms  based on an exogeneous response variable. 

## Overview

The most important functions in **SentimentAnalysis** are:

* ...

## Installation

Using the **devtools** package, you can easily install the latest development version of **SentimentAnalysis** with

```{r,eval=FALSE}
install.packages("devtools")

# Option 1: download and install latest version from ‘GitHub’
devtools::install_github("sfeuerriegel/SentimentAnalysis")

# Option 2: install directly from bundled archive
# devtoos::install_local("SentimentAnalysis_1.0.0.tar.gz")
```

Notes: 

* In the case of option 2, you have to specify the path either to the directory of **SentimentAnalysis** or to the bundled archive **SentimentAnalysis_1.0.0.tar.gz**

* A CRAN version has not yet been released.
